%SourceDoc ../YourName-Dissertation.tex
\vspace*{-80mm}
\chapter{Introduction} \label{chapter1:introduction}

For the past several decades, the primary focus in nuclear engineering within
the United States has been on light water reactors (LWR). Commercially,
all nuclear reactors are either boiling water reactors (BWR) or pressurized
water reactors (PWR). Correct computation of the thermal hydraulics within the
reactor core leads to efficient design and accuracy in the safety analysis. 
CASL is a key player in the effort, and utilizes the popular subchannel code,
CTF, for modeling the hydrodynamics within the reactor core \cite{Schmidt2014}.
This FORTRAN based code developed from COBRA-TF solves 8 conservation equations
for liquid, entrained droplet, and vapor phases phases, plus one conservation
equation for non-condensable gases \cite{CTF_theory}. The set of procedures
for ensuring that simlution codes such as CTF are accurate and reliable is
called software validation and verification \cite{Oberkampf2008}. CTF has
continually undergone software uncertiainty quantificaiton and benchmark
validation \cite{Avramova2015}. The current version of CTF has standard verification
practices that focus on software quality engineering similar to those in other
versions of COBRA-TF \cite{Aumiller2013}, but currently lacks an in depth
verification document that focuses on numerical algorithm verification.
This work focuses on this second type of verification for the original version
of CTF as well as a residual formulation. The 1-D residual formulation of the
code has been created for single phase liquid coupled to radial conduction.
While other residual formulations have been formed for other versions of
COBRA-TF \cite{Lloyd2014}, none have been integrated into the CASL version of
CTF. This work details the verification of both the residual formulation and the
original version of CTF for the single phase liquid and radial conduction
equations. The verification problems will study of the order of accuracy of the
errors, which is considered one of the more rigorous verification criteria
\cite{Roy2005}. This work will be considered a starting point for future work to
perform verification on the single phase equations in both axial and transverse
dimensions \cite{Merroun2009}, and two phase flow \cite{Mahadevan2009}.

%\section{CTF}